### 2017-08-23 article/article.tex
Initial commit

\documentclass[UTF8]{ctexart}
\author{李昂}
\title{基于卷积神经网络的图像识别}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{url}
\usepackage{geometry}
\usepackage{appendix}
\usepackage{booktabs}
\usepackage{cases}
\usepackage{graphicx}
\usepackage{subfigure}
\usepackage{listings}
\usepackage{xcolor}
\usepackage{fancyhdr}

\pagestyle{fancy}
\lhead{}
\chead{}
\rhead{}
\lfoot{}
\cfoot{\thepage}
\rfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\linespread{1.5}
\geometry{left=2.5cm,right=2.5cm,top=2.5cm,bottom=2.5cm}
\bibliographystyle{gbt7714-2005}

\begin{document}
\maketitle
\begin{abstract}
这里是摘要。
\begin{flushleft}
\textbf{关键词：} 卷积神经网络; 深度学习; 图像识别
\end{flushleft}
\end{abstract}

\clearpage

\section{问题背景与分析}
\subsection{背景}

\end{document}